Magnitude of simple rules in investment strategies of algorithmic trading

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
katalog na rysunki

\begin{table}[!t]
\caption{Profits for all strategy quadrants} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 26.177 & 5.5909868 & 24 & 2764\\ \hline 
S1b & -19.002 & -0.74976326 & 31 & 2801\\ \hline 
S1c & 12.025 & 2.6645247 & 31 & 2167\\ \hline 
S1d & -4.57 & -0.47001954 & 21 & 2226\\ \hline 
S1s & 14.33 & 2.957078 & NaN & 4968\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{S1a.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{S1b.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{S1c.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{S1d.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{S1s.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{EURJPY market results}
\end{figure}
\FloatBarrier

>>>>

\begin{table}[!t]
\caption{Profits for all strategy quadrants} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 26.177 & 5.5909868 & 24 & 2764\\ \hline 
S1b & -14.774 & -0.67029627 & 6 & 2660\\ \hline 
S1c & 15.736 & 2.4898734 & 6 & 2332\\ \hline 
S1d & -4.57 & -0.47001954 & 21 & 2226\\ \hline 
S1s & 22.54 & 3.2459677 & NaN & 4975\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

\begin{figure}[h]
\centering
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1a_eurjpy.eps}
\subcaption{Profit - S1a}
\label{jedno}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1b_eurjpy.eps}
\subcaption{Profit - S1b}
\label{dwu}
\end{minipage}
\\
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1c_eurjpy.eps}
\subcaption{Profit- S1c}
\label{cztero}
\end{minipage}
\begin{minipage}{.49\linewidth}
\centering 
\includegraphics[width=0.82\textwidth]{images/S1d_eurjpy.eps}
\subcaption{Profit - S1d}
\label{mansard}
\end{minipage}
\begin{minipage}{\linewidth}
\centering 
\includegraphics[width=0.6\textwidth]{images/S1s_eurjpy.eps}
\label{mansard}
\subcaption{Profit - S1s}
\end{minipage}
\caption{EURJPY market results}
\end{figure}
\FloatBarrier
